Helmet Foam Case Study Report

### 2024-05-07 CS2 Final Draft.qmd
Update CS2 Final Draft.qmd

|    Stiffness Model Predictors    |        Damping Model Predictors                     
|:---------------------------------|:------------------------------------|
           chemIndex               |             chemIndex
             freq                  |               freq
          log(cycle)               |            log(cycle)
              amp                  |             porosity
       chemIndex:log(cycle)        |         chemIndex:log(cycle)
        freq:log(cycle)            |           freq:log(cycle)
        amp:log(cycle)             |         porosity:log(cycle)

@@

$\beta_i = \beta_0 + \beta_1*\text{chemIndex} +\beta_2*\text{freq}$

@@

\begin{center}
\text{Table 6: Coefficients for Damaping Fraction Model}
\end{center}

@@

>>>>

|    Stiffness Model Predictors    |        Damping Model Predictors                     
|:---------------------------------|:------------------------------------|
           chemIndex               |             chemIndex
             freq                  |               freq
          log(cycle)               |            log(cycle)
              amp                  |         chemIndex:log(cycle)
       chemIndex:log(cycle)        |          freq:log(cycle)
        freq:log(cycle)            |           
        amp:log(cycle)             |

@@

$\beta_i = \beta_0  + \beta_2*\text{chemIndex} +\beta_3*\text{freq}$

@@

\begin{center}
\text{Table 7: Coefficients for Damaping Fraction Model}
\end{center}

@@

\begin{center}
\text{Table 8: Anova Analysis of Damping Fraction Model}
\end{center}
